---
title: "hw0"
author: "Ellie Zhang"
format: html
editor: visual
---

## Define the equation we want to solve and set values for its variables

-   Set values for the variables a, b, and c (in this example we have a = 1, b = 3, c = 2)

-   Set the quadratic equation as $f(x) = ax^2 + bx + c = 0$

```{r}
#| echo: false
a <- 1
b <- 3
c <- 2
fx <- function(x) {a*x^2 + b*x + c}
```

## Calculate the solution(s) of the quadratic equation

-   Calculate the discriminate of the quadratic equation as $discriminant = b^2 - 4ac$
    -   If $discriminant = 0$, the equation has one real solution
    -   If $discriminant > 0$, the equation has two real solutions
    -   If $discriminant < 0$, the equation has zero real solution
-   Calculate and return the solution(s) using the formula $x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}$, and if there is no real solution, return NA

```{r}
#| echo: false
sol <- function(a, b, c) {
  discrim <- b^2 - 4*a*c
  if (discrim == 0) {
    return(-b / (2*a))
  } else if (discrim > 0) {
    return(c((-b + sqrt(b^2 - 4*a*c)) / (2*a), 
             (-b - sqrt(b^2 - 4*a*c)) / (2*a)))
  } else {
    return(NA)
  }
}
sol(a, b, c)
```

## Plot the quadratic equation to confirm the result

-   Create a graph of f(x) versus x for $x\in(-5, 5)$

-   Draw a horizontal line on the graph at f(x) = 0

-   The intersection point(s) between the curve and the horizontal line represents the real solution(s) of the quadratic equation

```{r}
#| echo: false
x <- seq(-5, 5, length = 300)
plot(x, fx(x), type = "l")
abline(h = 0, lty = 2)
```
